### 2016-10-27 thesis/intro/intro.tex
tmp commit

% General intro to obesity.
% Implications of obesity -- disease associated with it and/or cancer.
Obesity has been one of the major global problems for more than a decade, associated with many noncommunicable diseases such as diabetes, cardiovascular diseases and certain types of cancers \citep{WHO2014}.
In fact, the risk of comorbidities increases with the increase in \gls{bmi}, where the risk becomes severe as the \gls{bmi} level approaches the obese category (citation).

The number of overweight and obese population, in both adults and children, have risen in every country of the world, and the trend continues as we speak.
Estimated to account for 3.4 million deaths per year and 93.6 million \glspl{daly} in 2010, obesity is a serious disease that continues to grow in our society, which the world cannot ignore (citation from 2010 WHO report needed).

@@

@@

@@

\subsection{Preventive measure of obesity}
\label{sub:preventive_measure_of_obesity}

>>>>

% General intro to obesity.
% Implications of obesity -- disease associated with it and/or cancer.
Obesity has been one of the major global problems for more than a decade, associated with many noncommunicable diseases such as diabetes, cardiovascular diseases and certain types of cancers \citep{WHO2014}.
In fact, the risk of comorbidities increases with the increase in \gls{bmi}, where the risk becomes severe as the \gls{bmi} level approaches the obese category (citation from 2000 WHO).

The number of overweight and obese population, in both adults and children, have risen in every country of the world, and the trend continues as we speak.
Estimated to account for 3.4 million deaths per year and 93.6 million \glspl{daly} in 2010, obesity is a serious disease that continues to grow in our society (citation from 2010 WHO report needed).

@@

Obesity is caused by excessive intake of energy without expending the energy gained.
As one can suspect, there are many factors involved with the likelihood of an individual to become overweight and obese.

\subsubsection{Individual-level (micro-level) factors}
\label{ssub:Individual-level (micro-level) factors}

There are many genetic evidence of obesity being caused by individual-level factors that makes some individuals more predisposed (right word??) to obesity than others (citation).
\textit{Talk about individual-level factors that affect obesity here (need citations on individual factors of obesity; e.g. genetic variation).}

\subsubsection{Population-level (macro-level) factors}
\label{ssub:Population-level (macro-level) factors}

Even though some individual-level factors are involved with obesity, it is clear that these individual-level factors cannot be accounted for the global epidemic of obesity that the world observes.
For this reason, obesity is thought to be caused mainly by the environmental factors that are present in the population.

The first key factor that contirbutes to the global rise in obese population is the availability and abundance of certain food in the country.

\textit{(Expand on this -- better trades around the globe (?)) \citep{Kearney2010, Malik2013}}

The second factor to consider is the behavioural changes led by the urbanisation of the population.
\textit{(Expand on this -- physical activity, sociocultural norm, etc.\citep{Malik2013})}

The third factor is the income and socioeconomic status of the countries.
\textit{(Expand on this -- rise in income, availability of health care, etc.\citep{Malik2013})}

The last factor, which ties in strongly with the first key factor, is the choice of diet by the population.
\textit{(Expand on this -- increased variety of food, low quality and high energy food choice, etc.)}

@@

As mentioned at the beginning of the current section, obesity has a devastating effect on the health of the population globally.

@@

\subsection{Preventive measures of obesity}
\label{sub:preventive_measures_of_obesity}
